Hemispheric Lateralization in ICH

### 2023-05-18 code/dataAnalysis/02analysis.qmd
euroQOL

>>>>

euroQOLCounts <- d |>
  filter(!is.na(euroMobility90)) |>
  group_by(ichLaterality, euroMobility90) |>
  tally(name = "patients") |>
  group_by(ichLaterality) |>
  mutate(percentPatients = patients / sum(patients)) |>
  ungroup() |>
  mutate(percentPatientsLabel = percent(percentPatients, accuracy = 1))

ggplot(
  data = euroQOLCounts,
  aes(x = ichLaterality, y = percentPatients, fill = euroMobility90)
) +
  geom_bar(stat = "identity", position = "fill", width = 0.5) +
  geom_text(aes(label = patients),
    position = position_stack(vjust = 0.5),
    color = "white",
    size = 5,
    family = "FigTree"
  ) +
  coord_flip() +
  scale_y_continuous(
    name = NULL,
    labels = scales::percent_format(accuracy = 1),
    breaks = c(seq(0, 1, 0.2))
  ) +
  scale_x_discrete(name = NULL) +
  # scale_fill_viridus_c() +
  labs(
    title = "Hemispheric Laterality",
    subtitle = "euroMobility90"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 30, lineheight = 0.1),
    plot.subtitle = element_text(size = 20, lineheight = 0.1),
    plot.caption = element_text(size = 20),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    legend.title = element_blank(),
    legend.position = "right",
    legend.text = element_text(size = 15, lineheight = 0.5),
    # legend.margin = margin(r = 50),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    axis.text.y = element_text(size = 20, lineheight = 0.5, margin = margin(r = -10)),
    axis.title.x = element_text(size = 20, lineheight = 0.5)
  )
